The great codivergence bake off

### 2024-12-11 manuscript/ms.tex
Accepted track changes on Overleaf

In their study into the factors affecting the divergence of flightless darkling beetles across the Aegean Archipelago,
Papadopoulou and Knowles \citeyear{PapadopoulouKnowles2015} used \dppmsbayes to estimate the relative divergence times of 13 pairs of populations that vary phenotypically and ecologically.
Their dataset included two Sanger loci --- one mitochondrial (Cox1; \textit{n} = 403) and one nuclear (Mp20; \textit{n} = 273)--- sequenced across hundreds of beetles from 60 localities on the 11 islands on the Cycladic plateau in the Aegean archipelago \citep{PapadopoulouKnowles2015}.
\jrocomment{We should probably describe the dataset a bit; number of loci, etc.}

>>>>

In their study into the factors affecting the divergence of flightless darkling beetles across the Aegean Archipelago,
Papadopoulou and Knowles \citeyear{PapadopoulouKnowles2015} used \dppmsbayes to estimate the relative divergence times of 13 pairs of populations that vary phenotypically and ecologically.
Their dataset included two Sanger loci --- one mitochondrial (Cox1; \textit{n} = 403) and one nuclear (Mp20; \textit{n} = 273)--- sequenced across hundreds of beetles from 60 localities on 11 islands of the Cycladic plateau in the Aegean archipelago \citep{PapadopoulouKnowles2015}.
\jrocomment{We should probably describe the dataset a bit; number of loci, etc.}
